---
title: "Euros 2024 Rankings"
date: 'Last updated: `r format(Sys.Date())`'
output:
  html_document:
    dpi: 500
    fig_width: 10
    fig_height: 7
---


```{r setup, include=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE)
```

## Top 50 Football Rankings

```{r Setup , echo =FALSE}

library(tidyverse)
library(ggimage)
library(glue)
library(ggtext)
library(reactable)
library(reactablefmtr)


# Optional but makes R prefer not to display numbers in scientific notation
options(scipen = 9999)

# load rankings and team mapping files
rankings <- read_csv('rankings.csv')
team_mapping <- read_csv('team_mapping.csv')


# Make Reactable table
rankings %>%
  slice(1:50) %>%
  left_join(team_mapping) %>%
   mutate(
    net_rating_cols = case_when(net_rating >= 0 ~ "darkgreen",
                         TRUE ~ "red")
    ) %>%
  select(rank, flag_logo, team, group, offense:net_rating_cols) %>%
  reactable::reactable(
    pagination = FALSE,
    searchable = TRUE,
    defaultSorted = 'rank',
    defaultSortOrder = 'asc',
    columns = list(
      rank = colDef(name = "Rank"),
      #flag_logo = colDef(name = ""),
      team = colDef(name = "Team"),
      group = colDef(name = "Group"),
      offense = colDef(name = "Offense",
                       format =  colFormat(digits = 2)),
      defense = colDef(name = "Defense",
                       format =  colFormat(digits = 2)),
      # net_rating = colDef(name = "Net Rating",
      #                     format =  colFormat(digits = 2),
      #                     style = color_scales(rankings, colors = paletteer::paletteer_d(
      #                                    palette = "ggsci::amber_material")
      #                                    )
      #   ),
      net_rating = colDef(name = "Net Rating",
                maxWidth = 80,
                # conditionally colored text using reactablefmtR
                cell = pill_buttons(., number_fmt = function(value) sprintf("%+0.1f", value), colors = "transparent", opacity = 0, bold_text = TRUE, text_color_ref = "net_rating_cols"),
                # add a solid border to the right-hand side of the column
                style = list(borderLeft = "1px solid #777")
              ),
      net_rating_cols = colDef(show = FALSE),
      flag_logo = colDef(name = "",
                         maxWidth = 70,
                         align = "center",
                         cell = embed_img(height = "25", width = "30")
                      )
      )
    )
